\documentclass[]{article}
\title{Assignment 10 - Git}
\date{\today}
\begin{document}
\maketitle
\section{Movie 1 - 3 Idiots}
This moive was directed by RajKumar Hirani.
A great part of the film's appeal is Aamir Khan, who has come to specialize in heroic iconoclasts, such as a rebellious villager in "Lagaan" or a visionary teacher of special-needs kids in "Taare Zameen Par." As Rancho, a young engineer of dazzling inventiveness, Khan conveys smarts, mischief and, finally, compassion, as he spurs his friends on to greatness before he mysteriously disappears.

The film's good points, though, are marred by a slow start and a nerve-jangling soundtrack (except for the charming "Aal Izz Well"). Perceptive, subtle acting work by Khan, Madhavan and Joshi also clashes with buffoonish performances by Omi Vaidya, as an odious school rival, and veteran character actor Irani, whose character is cursed with an unnecessary -- and unfunny -- lisp.

Hirani's screenplay also jumps back and forth in time over a 10-year period with limited success, leaving the viewer often wondering whether we're seeing scenes set in the present or the past.

Despite its flaws, "3 Idiots" conveys a powerful message about how valuable your friends can be when they push you toward reaching your own highest potential.
I would personnaly rate this movie 9/10. :)

\section{Movie 2}
In plain and simple words, I loved CDI. Heck, even if you take SRK out of it, I would still love it! This movie is about a man trying to prove his dedication and love for his sport, his people, and his country. This is about a man scorned by the nation, shunned by his close ones, and his redemption in the way he knows best. Its this main underlying theme that makes CDI special. This theme is so universal, and so identifiable, that your heart connects instantly.

CDI is about Indian sportswomen coming to the forefront, about the stark and grim realities staring at our national sport, and the reasons behind that. It is about unity in diversity, strength in weakness, and putting the team above oneself. Its about the sacrifices one has to make in order to achieve his goals. Its about the success of true sporting spirit! Its real, yet entertaining. Its patriotic without being jingoistic. Its international, yet soaked in Indianness. Its a collage of the different states of India, and the difficult but fruitful formation of this collage.

I have never played or watched or been interested in hockey! But this movie does not need that to touch your heart. All it needs is some patriotism, humility and goodness in your heart. If thats in abundance, I am sure you will love it.

As for the performances, I would just say the entire team rocks. the keyword here is TEAM, as thats what this film is all about! Enjoy !
\end{document}
